### 2018-07-17 paper/security-discussion.tex
Removes treated comments in security discussion

This means that under the assumption of uniformly random peer sampling, we 
achieve the properties we outlined in \cref{system-model}.
Additionally, since Alice and Bob choose a new key for every file, we have 
forward secrecy between files.
\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
sent to Bob, unless it is an ongoing transfer.
\\
%\subsection{Limitations}%
\label{security-limitations}

@@

\commentDaniel{We need to prove that our POR still fulfil the CL definition of 
  OR.
  Since they formalize and idealize ordinary OR we need to see that our changes 
  still work.}

\commentDaniel{Retransmission is not captured in the CL OR-model, that's fine 
  since packets are dropped.
  We must capture the behaviour that if the adversary interrupts transmission, 
  we will try to send to another node.
  We can probably fix this by outputting all nodes in the next layer in the 
  ideal model.}

>>>>

This means that under the assumption of uniformly random peer sampling, we 
achieve the properties we outlined in \cref{system-model}.
Additionally, since Alice and Bob choose a new key for every file, we have 
forward secrecy between files.
\Eg an adversary who compromises either Alice or Bob cannot determine what Alice 
sent to Bob, unless it is an ongoing transfer.

\paragraph*{Limitations}%
\label{security-limitations}

@@
